Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-17 code/analysis.Rmd
done with appendix

  ggplot(aes(x = t, y = resid), data = dataset) +
    geom_point() +
    theme_bw() +
    theme(plot.title = element_text(hjust = .5)) +
    geom_hline(yintercept = 0, color = "black") +
    geom_smooth(color = "red") +
    labs(x = "Time (s)", y = "Residual Value") +
    ggtitle(title)

>>>>

  ggplot(aes(x = t, y = resid), data = dataset) +
    geom_point(alpha = .5) +
    theme_bw() +
    theme(plot.title = element_text(hjust = .5)) +
    geom_hline(yintercept = 0, color = "black") +
    geom_smooth(color = "red") +
    labs(x = "Time (s)", y = "Residual Value") +
    ggtitle(title)
